---
title: "Peak_calling_with _pvalue"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Packages
```{r echo=FALSE}
setwd('/home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/rscripts/')
library(tidyverse)
library(ggplot2)
library(DESeq2)
library(GenomicRanges)
library(GenomeInfoDb)
library(circlize)
library(GenomicAlignments)
library(rtracklayer)
library(ChIPseeker)
library(TxDb.Mmusculus.UCSC.mm10.knownGene)
txdb <- TxDb.Mmusculus.UCSC.mm10.knownGene
library(clusterProfiler)
library(ChIPpeakAnno)
library(ReactomePA)
library(tibble)
library(ggpubr)
library(DiffBind)
library(org.Mm.eg.db)
library(diffloop)
library(ggrepel)
library(pheatmap)
library(apeglm)
library(readr)
library(biomaRt)
library(TxDb.Mmusculus.UCSC.mm10.knownGene)
library(Biostrings)
library(GenomicRanges)
library(BSgenome.Mmusculus.UCSC.mm10)
library(TFBSTools)
library(JASPAR2020)
library(SummarizedExperiment)
library(grid)
library(gdata)
```

create conda environment (I will use the one created from davide)
```{bash}
```{bash}
conda create --name seacr 

conda install --name seacr -c bioconda r-base=4.2.1
conda install --name seacr -c bioconda bedtools=2.30.0
conda install --name seacr -c bioconda seacr=1.3
conda install --name seacr -c bioconda deeptools=3.5.1

```
list env and connect
```{bash}
conda env list

source activate seacr

conda deactivate

```

# run seacr to call. peaks without IgG control based of 0.01 pvalue cutoff


```{bash}

#0.01
SEACR_1.3.sh /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/nextflow_output_CPM/03_peak_calling/01_bam_to_bedgraph/DMSO_Flag_R1.sorted.bedGraph 0.01 non stringent /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R1_p0.01.peaks


SEACR_1.3.sh /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/nextflow_output_CPM/03_peak_calling/01_bam_to_bedgraph/DMSO_Flag_R2.sorted.bedGraph 0.01 non stringent /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R2_p0.01.peaks


SEACR_1.3.sh /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/nextflow_output_CPM/03_peak_calling/01_bam_to_bedgraph/DMSO_Flag_R3.sorted.bedGraph 0.01 non stringent /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R3_p0.01.peaks
```

```{bash}

#0.001
SEACR_1.3.sh /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/nextflow_output/03_peak_calling/01_bam_to_bedgraph/DMSO_Flag_R1.sorted.bedGraph 0.001 non stringent /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R1_p0.001.peaks


SEACR_1.3.sh /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/nextflow_output/03_peak_calling/01_bam_to_bedgraph/DMSO_Flag_R2.sorted.bedGraph 0.001 non stringent /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R2_p0.001.peaks


SEACR_1.3.sh /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/nextflow_output/03_peak_calling/01_bam_to_bedgraph/DMSO_Flag_R3.sorted.bedGraph 0.001 non stringent /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R3_p0.001.peaks
```



```{bash}

#0.05
SEACR_1.3.sh /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/nextflow_output/03_peak_calling/01_bam_to_bedgraph/DMSO_Flag_R1.sorted.bedGraph 0.05 non stringent /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R1_p0.05.peaks


SEACR_1.3.sh /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/nextflow_output/03_peak_calling/01_bam_to_bedgraph/DMSO_Flag_R2.sorted.bedGraph 0.05 non stringent /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R2_p0.05.peaks


SEACR_1.3.sh /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/nextflow_output/03_peak_calling/01_bam_to_bedgraph/DMSO_Flag_R3.sorted.bedGraph 0.05 non stringent /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R3_p0.05.peaks
```

converrt to bedgraphs
```{bash}
awk '{ print $1"\t"$2"\t"$3"\t"$5 }' DMSO_Flag_R1_p0.01.peaks.stringent.bed > DMSO_Flag_R1_p0.01.peaks.stringent.bedGraph


awk '{ print $1"\t"$2"\t"$3"\t"$5 }' DMSO_Flag_R2_p0.01.peaks.stringent.bed > DMSO_Flag_R2_p0.01.peaks.stringent.bedGraph

awk '{ print $1"\t"$2"\t"$3"\t"$5 }' DMSO_Flag_R3_p0.01.peaks.stringent.bed > DMSO_Flag_R3_p0.01.peaks.stringent.bedGraph

rsync -aP hgdownload.soe.ucsc.edu::genome/admin/exe/linux.x86_64/bedGraphToBigWig ./

/home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/bedGraphToBigWig /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R1_p0.01.peaks.stringent.bedGraph chrom.sizes DMSO_Flag_R1_p0.01.peaks.bigWig

/home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/bedGraphToBigWig /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R2_p0.01.peaks.stringent.bedGraph chrom.sizes DMSO_Flag_R2_p0.01.peaks.bigWig

/home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/bedGraphToBigWig /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R3_p0.01.peaks.stringent.bedGraph chrom.sizes DMSO_Flag_R3_p0.01.peaks.bigWig




```


converrt to bedgraphs
```{bash}
awk '{ print $1"\t"$2"\t"$3"\t"$5 }' DMSO_Flag_R1_p0.001.peaks.stringent.bed > DMSO_Flag_R1_p0.001.peaks.stringent.bedGraph


awk '{ print $1"\t"$2"\t"$3"\t"$5 }' DMSO_Flag_R2_p0.001.peaks.stringent.bed > DMSO_Flag_R2_p0.001.peaks.stringent.bedGraph

awk '{ print $1"\t"$2"\t"$3"\t"$5 }' DMSO_Flag_R3_p0.001.peaks.stringent.bed > DMSO_Flag_R3_p0.001.peaks.stringent.bedGraph

rsync -aP hgdownload.soe.ucsc.edu::genome/admin/exe/linux.x86_64/bedGraphToBigWig ./

/home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/bedGraphToBigWig /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R1_p0.001.peaks.stringent.bedGraph chrom.sizes DMSO_Flag_R1_p0.001.peaks.bigWig

/home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/bedGraphToBigWig /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R2_p0.001.peaks.stringent.bedGraph chrom.sizes DMSO_Flag_R2_p0.001.peaks.bigWig

/home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/bedGraphToBigWig /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R3_p0.001.peaks.stringent.bedGraph chrom.sizes DMSO_Flag_R3_p0.001.peaks.bigWig




```
converrt to bedgraphs
```{bash}
awk '{ print $1"\t"$2"\t"$3"\t"$5 }' DMSO_Flag_R1_p0.05.peaks.stringent.bed > DMSO_Flag_R1_p0.05.peaks.stringent.bedGraph


awk '{ print $1"\t"$2"\t"$3"\t"$5 }' DMSO_Flag_R2_p0.05.peaks.stringent.bed > DMSO_Flag_R2_p0.05.peaks.stringent.bedGraph

awk '{ print $1"\t"$2"\t"$3"\t"$5 }' DMSO_Flag_R3_p0.05.peaks.stringent.bed > DMSO_Flag_R3_p0.05.peaks.stringent.bedGraph

#rsync -aP hgdownload.soe.ucsc.edu::genome/admin/exe/linux.x86_64/bedGraphToBigWig ./

/home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/bedGraphToBigWig /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R1_p0.05.peaks.stringent.bedGraph chrom.sizes DMSO_Flag_R1_p0.05.peaks.bigWig

/home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/bedGraphToBigWig /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R2_p0.05.peaks.stringent.bedGraph chrom.sizes DMSO_Flag_R2_p0.05.peaks.bigWig

/home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/bedGraphToBigWig /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R3_p0.05.peaks.stringent.bedGraph chrom.sizes DMSO_Flag_R3_p0.05.peaks.bigWig




```



Copare bigwigfiles to mm10
```{bash}
computeMatrix reference-point -S /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R1_p0.01.peaks.bigWig /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R2_p0.01.peaks.bigWig /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R3_p0.01.peaks.bigWig -R /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/TSS-TES_mm10_VM23.bed -a 3000 -b 3000 -o /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/test.gz -p 12 --missingDataAsZero

plotProfile -m /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/test.gz -out /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/test.pdf --perGroup --samplesLabel R1 R2 R3 -T "T" --legendLocation upper-left --plotHeight 12 --plotWidth 18 --plotFileFormat "svg"

```





Compare bigwigfiles to center of top 10 peaks
```{bash}
computeMatrix reference-point -S /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R1_p0.01.peaks.bigWig /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R2_p0.01.peaks.bigWig /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R3_p0.01.peaks.bigWig /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/nextflow_output/03_peak_calling/03_bed_to_bigwig/DMSO_IgG_R2.bigWig -R /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/rscripts/data/top10prChIP.bed -a 3000 -b 3000 -o /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/overtop10_newly_called_peaks.gz -p 12 --missingDataAsZero --referencePoint center


plotProfile -m /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/overtop10_newly_called_peaks.gz -out /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/overtop10_newly_called_peaks.pdf --perGroup --samplesLabel  R2 R3 IgG -T "T" --legendLocation upper-left --plotHeight 12 --plotWidth 18 --plotFileFormat "svg"



computeMatrix reference-point -S /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R1_p0.01.peaks.bigWig /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R1_p0.001.peaks.bigWig /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R1_p0.05.peaks.bigWig /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/nextflow_output/03_peak_calling/03_bed_to_bigwig/DMSO_IgG_R1.bigWig -R /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/rscripts/data/top10prChIP.bed -a 3000 -b 3000 -o /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/overtop10_newly_called_peaks_pvalues.gz -p 12 --missingDataAsZero --referencePoint center


plotProfile -m /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/overtop10_newly_called_peaks_pvalues.gz -out /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/overtop10_newly_called_peaks_pvalue.svg --perGroup --samplesLabel  "pvalue 0.01" "pvalue 0.001" "pvalue 0.05" IgG -T "Comparison betweeen differently called peaks" --legendLocation upper-left --plotHeight 15 --plotWidth 24 --plotFileFormat "svg"

computeMatrix reference-point -S /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R1_p0.01.peaks.bigWig /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R1_p0.001.peaks.bigWig /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R1_p0.05.peaks.bigWig /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/nextflow_output/03_peak_calling/03_bed_to_bigwig/DMSO_IgG_R2.bigWig /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/ChIP_Ascl1/nextflow_output/bwa/mergedLibrary/bigwig/MmES_RVChIP_062_pv6_Ascl1_DBD_pool.bigWig -R /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/rscripts/data/top10prChIP.bed -a 3000 -b 3000 -o /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/overtop10_newly_called_peaks_pvalues_w_ChIP.gz -p 12 --missingDataAsZero --referencePoint center


plotProfile -m /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/overtop10_newly_called_peaks_pvalues_w_ChIP.gz -out /home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/overtop10_newly_called_peaks_w_ChIP.svg --perGroup --samplesLabel  "pvalue 0.01" "pvalue 0.001" "pvalue 0.05" IgG ChIP -T "Comparison betweeen differently called peaks" --legendLocation upper-left --plotHeight 12 --plotWidth 18 --plotFileFormat "svg"

```

import peaks to compare 

```{r}
CutnRun_peak_R1_IgG <- readPeakFile('/home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/rscripts/data/DMSO_Flag.consensus_2.bed')

ChIP_peaks<- readPeakFile('/home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/ChIP_Ascl1/nextflow_output/bwa/mergedLibrary/macs2/broadPeak/MmES_RVChIP_062_pv6_Ascl1_DBD_pool_peaks.broadPeak')

CutnRun_peak_R1_pvalue_0.001 <- readPeakFile('/home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R1_p0.001.peaks.stringent.bed')

CutnRun_peak_R1_pvalue_0.01 <- readPeakFile('/home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R1_p0.01.peaks.stringent.bed')

CutnRun_peak_R1_pvalue_0.05 <- readPeakFile('/home/ubuntu/MOUNT3/angela/xAT0007_cutandrun_StaPL/SEACR_calledpeaks/DMSO_Flag_R1_p0.05.peaks.stringent.bed')

```
# get the counts
```{r}

count_df <- data.frame(name = c("ChIP",
  "IgG (2/3)",
  "pvalue 0.05","pvalue 0.01",
                                "pvalue 0.001"), 
                       n = c(length(ChIP_peaks),
                         length(CutnRun_peak_R1_IgG),
                             length(CutnRun_peak_R1_pvalue_0.05),
                             length(CutnRun_peak_R1_pvalue_0.01),
                             length(CutnRun_peak_R1_pvalue_0.001)
                             ))
  count_df$name<- as.factor(count_df$name)
count_df$n <- as.numeric(count_df$n)
png("plots/number_peaks.png", width = 600, height = 400)
ggplot(count_df,aes(x=name, y=n))+geom_bar(stat= 'identity', fill="steelblue")+
  labs(title="Number of Peaks",x="", y = "Count",size=5)+theme_minimal() +geom_text(aes(label=n),position=position_dodge(0.9),vjust=-0.2, size=5)+ theme(plot.title = element_text(size=22), axis.title = element_text(size= 15),legend.text =element_text(size= 15),legend.title =element_text(size= 15) ,axis.text = element_text(size= 10) )
dev.off()

png("plots/Venndiagram_peakcalling.png", height = 500, width = 500)
makeVennDiagram(Peaks=list(CutnRun_peak_R1_IgG,CutnRun_peak_R1_pvalue_0.05,
                                  CutnRun_peak_R1_pvalue_0.01),
                       NameOfPeaks=c("IgG (2/3)", "pvalue 0.05","pvalue 0.01"), fill=c( "steelblue1","steelblue2","steelblue3"), cex = 1.5)
dev.off()

name = c("seacr ChIP",
  "Cutnrun IgG",
  "Cutnrun pvalue 0.05","Cutnrun pvalue0.01",
                                "Cutnrun pvalue 0.001")

# add width of each peak
ChIP_peaks$width <- width(ChIP_peaks)
CutnRun_peak_R1_IgG$width <- width(CutnRun_peak_R1_IgG)
CutnRun_peak_R1_pvalue_0.05$width <-  width(CutnRun_peak_R1_pvalue_0.05)
CutnRun_peak_R1_pvalue_0.01$width <- width(CutnRun_peak_R1_pvalue_0.01)
CutnRun_peak_R1_pvalue_0.001$width <- width(CutnRun_peak_R1_pvalue_0.001)


ChIP_peaks_df<- dplyr::select(as.data.frame(ChIP_peaks),width.1)
CutnRun_peak_R1_IgG_df<- dplyr::select(as.data.frame(CutnRun_peak_R1_IgG),width.1)
CutnRun_peak_R1_pvalue_0.05_df<- dplyr::select(as.data.frame(CutnRun_peak_R1_pvalue_0.05),width.1)
CutnRun_peak_R1_pvalue_0.01_df<- dplyr::select(as.data.frame(CutnRun_peak_R1_pvalue_0.01),width.1)
CutnRun_peak_R1_pvalue_0.001_df<- dplyr::select(as.data.frame(CutnRun_peak_R1_pvalue_0.001),width.1)


df <- cbindX(ChIP_peaks_df,CutnRun_peak_R1_IgG_df,CutnRun_peak_R1_pvalue_0.05_df,CutnRun_peak_R1_pvalue_0.01_df,CutnRun_peak_R1_pvalue_0.001_df)    
colnames(df)<- c("ChIP","CutnRunIgG (2/3)","CutNRun 0.05","CutNRun 0.01","CutNRun 0.001")
df_melt <- melt(df)

df_melt$variable <- as.factor(df_melt$variable)


df_melt[is.na(df_melt)] <- 0

png("plots/width_peaks.png", width= 600, height= 400)
ggplot(df_melt, aes(x=value, color= variable))+geom_density(size=1)+
  labs(title="Width of peaks",x="Width of peaks", y = "Density", colour="", size=5)+
  theme_minimal()+ scale_color_brewer(palette="Dark2")+ xlim(1,4000)+ theme(plot.title = element_text(size=22), axis.title = element_text(size= 15),legend.text =element_text(size= 15),legend.title =element_text(size= 15) ,axis.text = element_text(size= 10) )
dev.off()



median(ChIP_peaks$width)
median(CutnRun_peak_R1_IgG$width)
median(CutnRun_peak_R1_pvalue_0.05$width)
median(CutnRun_peak_R1_pvalue_0.01$width)
median(CutnRun_peak_R1_pvalue_0.001$width)
#258 chip
#311 IgG
#471 0.05
#900. 0.01
#854 0.001


```

see if Ascl1 is in these peaks

```{r}
mm10 <- BSgenome.Mmusculus.UCSC.mm10

pwms <- getMatrixSet(JASPAR2020, opts = list(matrixtype = "PWM", tax_group = "vertebrates"))
seqs_CutnRun_peak_R1_pvalue_0.05 <- getSeq(mm10, CutnRun_peak_R1_pvalue_0.05)

motif.enrichment.CutnRun_peak_R1_pvalue_0.05 <- calcBinnedMotifEnrR(seqs = seqs_CutnRun_peak_R1_pvalue_0.05,
                           pwmL = pwms,
                           background = "genome",
                           genome = mm10,
                           genome.regions = NULL, # sample from full genome
                           genome.oversample = 2, 
                           BPPARAM = BiocParallel::SerialParam(RNGseed = 42),
                           verbose = TRUE)

se.seq.motif.enrichment.CutnRun_peak_R1_pvalue_0.05 <- motif.enrichment.CutnRun_peak_R1_pvalue_0.05



ncol(motif.enrichment.CutnRun_peak_R1_pvalue_0.05)

# convert to data frame
df_se.seq.motif.enrichment.CutnRun_peak_R1_pvalue_0.05 <- rowData(se.seq.motif.enrichment.CutnRun_peak_R1_pvalue_0.05)


#select all motifs with Padj above a certain threshold. Modify to change stringency
sel.motif.enrichment.CutnRun_peak_R1_pvalue_0.05 <- assay(motif.enrichment.CutnRun_peak_R1_pvalue_0.05, "negLog10Padj")[, 1] > 5.0
sel.motif.enrichment.CutnRun_peak_R1_pvalue_0.05[is.na(sel.motif.enrichment.CutnRun_peak_R1_pvalue_0.05)] <- FALSE
df_se.seq.motif.enrichment.CutnRun_peak_R1_pvalue_0.05_log_2enr <- assay(motif.enrichment.CutnRun_peak_R1_pvalue_0.05[sel.motif.enrichment.CutnRun_peak_R1_pvalue_0.05,], "log2enr")

f<- as.data.frame(assay(motif.enrichment.CutnRun_peak_R1_pvalue_0.05,"log2enr"))
f<- rownames_to_column(f, "Motif")

f <- dplyr::filter(f,Motif== c("MA1100.1","MA1100.2"))
CutnRun_peak_R1_pvalue_0.01

png('plots/plotMotifHeatmaps_pvalue0.05.png',width= 800, height = 1200)

plotMotifHeatmaps(x = motif.enrichment.CutnRun_peak_R1_pvalue_0.05[sel.motif.enrichment.CutnRun_peak_R1_pvalue_0.05,], which.plots = c("log2enr"), maxEnr = 2, maxSig = 10,
                  show_dendrogram = TRUE,
                  show_seqlogo = TRUE,width.seqlogo = 1.2)
dev.off()

#MA1100.2	0.06757037

```
see if Ascl1 is in these peaks

```{r}
mm10 <- BSgenome.Mmusculus.UCSC.mm10
pfms.Ascl1 <- getMatrixByID(JASPAR2020, c("MA1100.1", "MA1100.2", "MA1631.1")) 

pwms_Ascl1  <- toPWM(pfms.Ascl1 )


Ascl1_motif.enrichment.CutnRun_peak_R1_pvalue_0.01 <- calcBinnedMotifEnrR(seqs = seqs_CutnRun_peak_R1_pvalue_0.01,
                           pwmL = pwms_Ascl1,
                           background = "genome",
                           genome = mm10,
                           genome.regions = NULL, # sample from full genome
                           genome.oversample = 2, 
                           BPPARAM = BiocParallel::SerialParam(RNGseed = 42),
                           verbose = TRUE)

se.seq.Ascl1_motif.enrichment.CutnRun_peak_R1_pvalue_0.01 <- Ascl1_motif.enrichment.CutnRun_peak_R1_pvalue_0.01



ncol(Ascl1_motif.enrichment.CutnRun_peak_R1_pvalue_0.01)

# convert to data frame
df_se.seq.Ascl1_motif.enrichment.CutnRun_peak_R1_pvalue_0.01 <- rowData(se.seq.Ascl1_motif.enrichment.CutnRun_peak_R1_pvalue_0.01)


#select all motifs with Padj above a certain threshold. Modify to change stringency
sel.Ascl1_motif.enrichment.CutnRun_peak_R1_pvalue_0.01 <- assay(Ascl1_motif.enrichment.CutnRun_peak_R1_pvalue_0.01, "negLog10Padj")[, 1] > 0.5
sel.Ascl1_motif.enrichment.CutnRun_peak_R1_pvalue_0.01[is.na(sel.Ascl1_motif.enrichment.CutnRun_peak_R1_pvalue_0.01)] <- FALSE
df_se.seq.Ascl1_motif.enrichment.CutnRun_peak_R1_pvalue_0.01_log_2enr <- assay(Ascl1_motif.enrichment.CutnRun_peak_R1_pvalue_0.01[sel.Ascl1_motif.enrichment.CutnRun_peak_R1_pvalue_0.01,], "log2enr")



png('plots/plotMotifHeatmaps_ASV_Flag.png',  
    width = 680, height = 1080,
    units = "px", pointsize = 12, bg = "white", res = NA)

plotMotifHeatmaps(x = Ascl1_motif.enrichment.CutnRun_peak_R1_pvalue_0.01[sel.Ascl1_motif.enrichment.CutnRun_peak_R1_pvalue_0.01,], which.plots = c("log2enr"), maxEnr = 0.7, maxSig = 10,
                  show_dendrogram = TRUE,
                  show_seqlogo = TRUE,width.seqlogo = 1.2)
dev.off()



```


see if Ascl1 is in these peaks also in ChIP

```{r}
mm10 <- BSgenome.Mmusculus.UCSC.mm10

pwms <- getMatrixSet(JASPAR2020, opts = list(matrixtype = "PWM", tax_group = "vertebrates"))
seqs_ChIP <- getSeq(mm10, ChIP_peaks)

motif.enrichment.ChIP <- calcBinnedMotifEnrR(seqs = seqs_ChIP,
                           pwmL = pwms,
                           background = "genome",
                           genome = mm10,
                           genome.regions = NULL, # sample from full genome
                           genome.oversample = 2, 
                           BPPARAM = BiocParallel::SerialParam(RNGseed = 42),
                           verbose = TRUE)

se.seq.motif.enrichment.ChIP <- motif.enrichment.ChIP



ncol(motif.enrichment.ChIP)

# convert to data frame
df_se.seq.motif.enrichment.ChIP <- rowData(se.seq.motif.ChIP)


#select all motifs with Padj above a certain threshold. Modify to change stringency
sel.motif.enrichment.ChIP <- assay(motif.enrichment.ChIP, "negLog10Padj")[, 1] > 150
sel.motif.enrichment.ChIP[is.na(sel.motif.enrichment.ChIP)] <- FALSE
df_se.seq.motif.enrichment.ChIP <- assay(motif.enrichment.ChIP[sel.motif.enrichment.ChIP,], "log2enr")

C<- as.data.frame(assay(motif.enrichment.ChIP,"log2enr"))
C<- rownames_to_column(C, "Motif")

C <- dplyr::filter(C,Motif== c("MA1100.1","MA1100.2"))

png('plots/plotMotifHeatmaps_ChIP.png',width= 800, height = 1200)

plotMotifHeatmaps(x = motif.enrichment.ChIP[sel.motif.enrichment.ChIP,], which.plots = c("log2enr"), maxEnr = 2, maxSig = 10,
                  show_dendrogram = TRUE,
                  show_seqlogo = TRUE,width.seqlogo = 1.2)
dev.off()

#MA1100.2	0.06757037
#MA1100.2	1.761352
```
for cutnRun Igg
```{r}


motif.enrichment.CutnRun_peak_R1_IgG <- calcBinnedMotifEnrR(seqs = seqs_CutnRun_peak_R1_IgG,
                           pwmL = pwms_Ascl1,
                           background = "genome",
                           genome = mm10,
                           genome.regions = NULL, # sample from full genome
                           genome.oversample = 2, 
                           BPPARAM = BiocParallel::SerialParam(RNGseed = 42),
                           verbose = TRUE)

se.seq.motif.enrichment.CutnRun_peak_R1_IgG <- motif.enrichment.CutnRun_peak_R1_IgG



ncol(motif.enrichment.CutnRun_peak_R1_IgG)

# convert to data frame
df_se.seq.motif.enrichment.CutnRun_peak_R1_IgG <- rowData(se.seq.motif.CutnRun_peak_R1_IgG)


#select all motifs with Padj above a certain threshold. Modify to change stringency
sel.motif.enrichment.CutnRun_peak_R1_IgG <- assay(motif.enrichment.CutnRun_peak_R1_IgG, "negLog10Padj")[, 1] > 0.5
sel.motif.enrichment.CutnRun_peak_R1_IgG[is.na(sel.motif.enrichment.CutnRun_peak_R1_IgG)] <- FALSE
df_se.seq.motif.enrichment.CutnRun_peak_R1_IgG <- assay(motif.enrichment.CutnRun_peak_R1_IgG[sel.motif.enrichment.CutnRun_peak_R1_IgG,], "log2enr")

P<- as.data.frame(assay(motif.enrichment.CutnRun_peak_R1_IgG,"log2enr"))
P<- rownames_to_column(P, "Motif")

P <- dplyr::filter(P,Motif== c("MA1100.1","MA1100.2"))

svg('plots/plotMotifHeatmaps_ChIP.png')

plotMotifHeatmaps(x = motif.enrichment.CutnRun_peak_R1_IgG[sel.motif.enrichment.CutnRun_peak_R1_IgG,], which.plots = c("log2enr"), maxEnr = 2, maxSig = 10,
                  show_dendrogram = TRUE,
                  show_seqlogo = TRUE,width.seqlogo = 1.2)
dev.off()

#MA1100.2	0.06757037 0.05
#MA1100.2	1.761352 chip

#MA1100.2	0.01181753	igg
#MA1100.2	0.03722239 0.01
```


```{r}
mm10 <- BSgenome.Mmusculus.UCSC.mm10

pwms <- getMatrixSet(JASPAR2020, opts = list(matrixtype = "PWM", tax_group = "vertebrates"))
seqs_CutnRun_peak_R1_pvalue_0.01 <- getSeq(mm10, CutnRun_peak_R1_pvalue_0.01)

motif.enrichment.CutnRun_peak_R1_pvalue_0.01 <- calcBinnedMotifEnrR(seqs = seqs_CutnRun_peak_R1_pvalue_0.01,
                           pwmL = pwms,
                           background = "genome",
                           genome = mm10,
                           genome.regions = NULL, # sample from full genome
                           genome.oversample = 2, 
                           BPPARAM = BiocParallel::SerialParam(RNGseed = 42),
                           verbose = TRUE)

se.seq.motif.enrichment.CutnRun_peak_R1_pvalue_0.01 <- motif.enrichment.CutnRun_peak_R1_pvalue_0.01



ncol(motif.enrichment.CutnRun_peak_R1_pvalue_0.01)

# convert to data frame
df_se.seq.motif.enrichment.CutnRun_peak_R1_pvalue_0.01 <- rowData(se.seq.motif.enrichment.CutnRun_peak_R1_pvalue_0.01)


#select all motifs with Padj above a certain threshold. Modify to change stringency
sel.motif.enrichment.CutnRun_peak_R1_pvalue_0.01 <- assay(motif.enrichment.CutnRun_peak_R1_pvalue_0.01, "negLog10Padj")[, 1] > 0.5
sel.motif.enrichment.CutnRun_peak_R1_pvalue_0.01[is.na(sel.motif.enrichment.CutnRun_peak_R1_pvalue_0.01)] <- FALSE
df_se.seq.motif.enrichment.CutnRun_peak_R1_pvalue_0.01_log_2enr <- assay(motif.enrichment.CutnRun_peak_R1_pvalue_0.01[sel.motif.enrichment.CutnRun_peak_R1_pvalue_0.01,], "log2enr")

g<- as.data.frame(assay(motif.enrichment.CutnRun_peak_R1_pvalue_0.01,"log2enr"))
g<- rownames_to_column(g, "Motif")

g <- dplyr::filter(g,Motif== c("MA1100.1","MA1100.2"))

png('plots/CutnRun_peak_R1_pvalue_0.01.png',width= 800, height = 1200)

plotMotifHeatmaps(x = motif.enrichment.CutnRun_peak_R1_pvalue_0.01[sel.motif.enrichment.CutnRun_peak_R1_pvalue_0.05,], which.plots = c("log2enr"), maxEnr = 2, maxSig = 10,
                  show_dendrogram = TRUE,
                  show_seqlogo = TRUE,width.seqlogo = 1.2)
dev.off()

#MA1100.2	0.06757037

```